Spatial Reasoning and Statistical Graphics

### 2014-10-20 Paper/Draft1/TestingVisualAptitude.Rnw
Subsection for scoring/scaling above the results section

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. 
\comment{Teensy overview of the demographics - this might end up in an appendix, but then we need to refer to from here. I'd like to know breakdown of men/women, classification, maybe an overview of different majors (not necessarily a breakdown, that might be leading to problems with identifiability)}
Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} from which parts of this test are drawn.

@@

>>>>

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. 
\comment{Teensy overview of the demographics - this might end up in an appendix, but then we need to refer to from here. I'd like to know breakdown of men/women, classification, maybe an overview of different majors (not necessarily a breakdown, that might be leading to problems with identifiability)}
\subsection{Scoring and Scaling of Answers}

Scoring of all test results was done such that random guessing leads to an expected value of 0; therefore each question answered correctly contributes to the score by 1, while a wrong answer is scored by $-1/(k-1)$, where $k$ is the total number of possible answers to the question. Thus, for a test consisting of multiple choice questions with $k$ suggested answers with a single correct answer each, the score is calculated as
\begin{eqnarray}\label{eq.scoring}
\# \text{correct answers } - 1/(k-1) \cdot \# \text{wrong answers}.
\end{eqnarray}
This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. Combining accuracy and speed into a single number does not only make a comparison of test scores easier,  this scoring mechanism is also used on many standardized tests, such as the SAT and the battery of psychological tests \citep{diamond1973correction, ekstrom1976manual} from which parts of this test are drawn.

@@

To facilitate comparison of the visuospatial skills tests utilized in this study with the lineups, we will scale the test results by a factor of $1/n \sqrt{k-1}$, where $n$ is the number of questions in a test and $k$ is the number of offered answers on each questions (out of which only one is correct). This scaling ensures that test scores across different types are comparable. All test scores are now normalized such that they have under the assumption of random guessing an expected value of zero and a standard deviation of 1. In particular, this leads to a theoretical range of a normalized test score $Z_{n, k}$ of $[-\sqrt{k-1}, \sqrt{k-1}]$.
